\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-08-14 Tex/PA_rrmemo/PA_RnR_memo.tex
wrote response to R1.1 and R1.2

%\title{Overleaf Memo Template}
% Using the texMemo package by Rob Oakes
\documentclass[a4paper,11pt]{texMemo}
\usepackage[english]{babel}
\usepackage{graphicx, lipsum}

%% Edit the header section here. To include your
%% own logo, upload a file via the files menu.
\memosubject{Manuscript Revisions for \emph{Political Analysis}}
\memoto{PA-2020-075}
\memofrom{Generative Dynamics of Supreme Court Citations: Analysis with a New Statistical Network Model}
\memodate{\today}

@@

@@

@@

>>>>

%\title{Overleaf Memo Template}
% Using the texMemo package by Rob Oakes
\documentclass[a4paper,11pt]{texMemo}
\usepackage[english]{babel}
\usepackage{graphicx, lipsum}
\usepackage{bm}
\usepackage[backend=bibtex]{biblatex}    
\usepackage[english]{babel}

\addbibresource{bib.bib}
%% Edit the header section here. To include your
%% own logo, upload a file via the files menu.
\memosubject{Manuscript Revisions for \emph{Political Analysis}}
\memoto{PA-2020-075}
\memofrom{Generative Dynamics of Supreme Court Citations: Analysis with a New Statistical Network Model}
\memodate{\today}

@@

\noindent \textbf{Addressed:} All networks were estimated using MCMLE, however, for smaller networks we used the network's MPLE as the algorithms's starting value, while for larger networks the starting value was obtained using simulated annealing, since the MPLE as starting value did not lead to converged MCMLEs anymore. While in theory the algorithm should converge to the MLE regardless of the starting value, in practice this is not the case   \cite{hummel2012improving}. \\
In order to be consistent with the used estimation approach, we estimate the MCMLE now for all networks using simulated annealing starting value. The results have not changed noticeably.  \\

@@

\noindent \textbf{Addressed:} We have re-estimated all networks using the simulated annealing approach and the results look very similar to the initially submitted results. This is not too surprising, since the MCMLE algorithm only reports a succesful estimation if it has converged to the unique MLE. However, with a poorly chosen starting value the algorithm might fail to converge towards the MLE. This is what happened for some large networks using the MPLE.  \\

@@

\printbibliography
